Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
runtimes -> running times

    \subsubsection{Runtimes of the algorithm}
    To be able to answer the runtime system without holding it up for too long, the scheduler needs to provide a fast answer.
    Our bottom-level-based heuristics \heftbl and \heftblc provide smaller runtimes and also scale better with growing workflow
    sizes~(see Fig.~\ref{fig:runtimes-abs} and Fig.~\ref{fig:runtimes-abs}).
    Their runtimes are similar and grow from tens of miliseconds for the smallest workflows to $25-27$ seconds for the largest workflows.
    \heftmm, however, needs to compute a memory-optimal traversal of the entire workflow to compute the ranks of the tasks,
    so its runtime scales from also rens of miliseconds for the smalest workflows to thousands of seconds - $1172.7$ for \numprint{20000}-task workflows and
    $2994.9$ seconds for the largest, \numprint{30000}-task workflows.
    This increased runtime is, though, offset by the unique $100\%$ success rate this algorithm shows when scheduling large
    workflows in difficult (memory-constrained) setups.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/runtimes-logarithmic}
        \caption{Runtimes of the heuristics and the baseline. The y axis ist logarithmic.}
        \label{fig:runtimes-log}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/runtimes-absolute}
        \caption{Runtimes of the heuristics and the baseline.}
        \label{fig:runtimes-abs}
        \vspace{-0.3cm}
    \end{figure}

@@

 \heftbl and \heftblc can schedule all workflows in a normal cluster and approximately a half of them in a memory-constrained
    one.
    They provide a runtime that scales well with the growing size of a workflow.

>>>>

    \subsubsection{Running times of the algorithm}
    To be able to answer the runtime system without holding it up for too long, the scheduler needs to provide a fast answer.
    Our bottom-level-based heuristics \heftbl and \heftblc provide smaller running times and also scale better with growing workflow
    sizes~(see Fig.~\ref{fig:runtimes-abs} and Fig.~\ref{fig:runtimes-abs}).
    Their running times are similar and grow from tens of miliseconds for the smallest workflows to $25-27$ seconds for the largest workflows.
    \heftmm, however, needs to compute a memory-optimal traversal of the entire workflow to compute the ranks of the tasks,
    so its runnning time scales from also rens of miliseconds for the smalest workflows to thousands of seconds - $1172.7$ for \numprint{20000}-task workflows and
    $2994.9$ seconds for the largest, \numprint{30000}-task workflows.
    This increased running time is, though, offset by the unique $100\%$ success rate this algorithm shows when scheduling large
    workflows in difficult (memory-constrained) setups.

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/runtimes-logarithmic}
        \caption{Running times of the heuristics and the baseline. The y axis ist logarithmic.}
        \label{fig:runtimes-log}
        \vspace{-0.3cm}
    \end{figure}

    \begin{figure}[tb]
        \centering
        \includegraphics[width=1.1\columnwidth] {images/runtimes-absolute}
        \caption{Running times of the heuristics and the baseline.}
        \label{fig:runtimes-abs}
        \vspace{-0.3cm}
    \end{figure}

@@

 \heftbl and \heftblc can schedule all workflows in a normal cluster and approximately a half of them in a memory-constrained
    one.
    They provide a running time that scales well with the growing size of a workflow.
